---
title: "Chaff"
author: "Megan Clark"
date: "04/11/2020"
output: 
  bookdown::pdf_document2: default
  bookdown::word_document2: default
  bookdown::html_document2: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE,
                      message = FALSE,
                      fig.retina = 3)
```

```{r packages}
library(tidyverse)
library(Rmisc)
library(tidyverse)
library(kableExtra)
library(gt)
library(flextable)
```

#Intro
#We decided to look into if the mean mass of chaffinches differ between male and female

#Methods
#We collected 20 samples of both male and female chaffinches and weighed them

#Discussion



# importing chaff data
chaff <- read.table("chaff.txt", header = TRUE)
chaff

#tidying data
chaff<- chaff%>% 
  pivot_longer(names_to = "sex", 
               values_to = "mass",
               cols = everything())

#summary of data
chaffsummary <- summarySE(chaff, measurevar = "mass",
                      groupvars = "sex")


#calculate the SS(x) for each group like this:
sum_sq <- function(df, measure, group) {
  df %>% group_by({{ group }}) %>% 
    summarise(ss = sum(({{measure}} - mean({{measure}}))^2))
}

sum_sq(chaff, mass, sex)

#summarising the masses by sex - 
#include the mean, standard deviation, sample size and the standard error
chaffsummary2 <- chaff %>% 
  group_by(sex) %>% 
  summarise(mean_mass = mean(mass),
            n = length(mass),
            sd = sd(mass),
            se = sd/sqrt(n))

#create a function called data_summary() that carries out that summarising? 
#You will need to use the double braces,{{ }}
chaffsummaryfunc <- function(ds, measure, group) {
  chaff %>% group_by(sex) %>% 
  summarise(mean_mass = mean(mass),
            n = length(mass),
            sd = sd(mass),
            se = sd/sqrt(n))
}
chaffsummaryfunc(chaff, mass, sex)









